{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-30 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

                    & & & E_1^Ty + z\\

@@

        \subsection{GMAPG main algorithm}
            % GMAPG ------------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function GMAPG Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                            $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
                            $x_{-1}$ & Vector\\
                            $L\in \RR$ & $L > 0$\\ 
                            $r $ & $r \in (0, 1)$ \\ 
                            $\rho \in \RR$ & $\rho \in (0, 1)$ \\
                            $N_{\min}\in \N$ & $N \ge 1$ \\
                            $N \in \N$ & $N \ge N_{\min}$ \\
                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 
                        \end{tabular}
                    }
                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = \Vert \sqrt{L_0}(x_0 - y_0)\Vert.$}
                    \IF{$G_0 \le \epsilon$}
                        \STATE{\textbf{Return: }$x_k, 0, L_0, G_0$}
                    \ENDIF
                    \FOR{$k := 1, 2,\ldots, N$}
                        \STATE{\noindent
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                        }
                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                        \STATE{\noindent
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        }
                        \STATE{$G_k:= \Vert \sqrt L_k(\tilde x_k - y_k)\Vert $}
                        \STATE{\noindent
                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        }
                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                            \STATE{\textbf{break}}
                        \ENDIF
                    \ENDFOR
                    \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
                \end{algorithmic}
            \end{algorithm}
            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
            For example, we chose $r= 0.4, \rho = 2^{1/1024}$.

@@

        A stronger result on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies \ref{ass:standard-fista}.

@@

                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G_k^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

        For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 

@@

            ...

@@

            Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^+_k \le \epsilon$ right at the start of iteration $J$.

@@

                &= \sum_{i = 0}^{m}n_i + \sum_{l = 0}^{n - 1}\sum_{i = 1}^{T_\epsilon} n_{m + i + lT}

@@

                \sum_{i = 0}^{J} n_i &\le 
                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} \left\lfloor 

@@

@@

        \begin{theorem}[convergence rates of restarted GMAPG]\label{thm:rgmapg-cnvg}

@@

>>>>

                    & & E_1^Ty & I_{n_1}\\

@@

        \subsection{GMAPG main algorithm}
            % GMAPG ------------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function GMAPG Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                            $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
                            $x_{-1}$ & Vector\\
                            $L\in \RR$ & $L > 0$\\ 
                            $r $ & $r \in (0, 1)$ \\ 
                            $\rho \in \RR$ & $\rho \in (0, 1)$ \\
                            $N_{\min}\in \N$ & $N \ge 1$ \\
                            $N \in \N$ & $N \ge N_{\min}$ \\
                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 
                        \end{tabular}
                    }
                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = \Vert \sqrt{L_0}(x_0 - y_0)\Vert.$}
                    \IF{$G_0 \le \epsilon$}
                        \STATE{\textbf{Return: }$x_k, 0, L_0, G_0$}
                    \ENDIF
                    \FOR{$k := 1, 2,\ldots, N$}
                        \STATE{\noindent
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                        }
                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                        \STATE{\noindent
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        }
                        \STATE{$G_k:= \Vert \sqrt L_k(\tilde x_k - y_k)\Vert $}
                        \STATE{\noindent
                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        }
                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                            \STATE{\textbf{break}}
                        \ENDIF
                    \ENDFOR
                    \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
                \end{algorithmic}
            \end{algorithm}
            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
            The first iterates $x_0$ is produced by a step of proximal gradient descent through Algorithm \ref{alg:armijo-ls} so, it has $x_0 = v_0 = T_{1/L_0}(x_{-1})$, and consequently all results from Theorem \ref{thm:gmapg-specialized-cnvg} apply. 
            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
            For example, we chose $r= 0.4, \rho = 2^{1/1024}$.

@@

        A stronger result on the convergence rate of $\Vert \mathcal G_{1/\eta_k}(y_k)\Vert$ can be obtained if, we assume that the function $F=f + g$ satisfies Assumption \ref{ass:standard-fista}.

@@

                \STATE{$z_{j + 1}, p_j, \overline L_{j + 1}, G^+ := \textbf{GMAPG}(f, g, z_j, \overline L_j, r, \rho, N_{\min}=n_j, N=M, \epsilon, \textbf{L}, \textbf{M}, \textbf{E}_{\chi}^a).$}

@@

        For example in line 10 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 

@@

            Let $F = f + g$ satisfies Assumption \ref{ass:q-growth-ch2}. 
            Suppose that Algorithm \ref{alg:linear-rgmapg} is applied to it then the total number of iterations is bounded for all $M \in \N$, $\epsilon > 0$ by
                \sum_{i = 0}^{J - 1}p_i &\le 
                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} \left\lceil 
                \right\rceil. 

@@

            Using it let's assume that it executed for $j = 1, 2, \cdots, J$ and $M$ is large enough to achieve optimality $G^+ \le \epsilon$ right at the start of iteration $J$.

@@

                &= \sum_{i = 0}^{m}n_i + \sum_{l = 0}^{n - 1}\sum_{i = 1}^{T_\epsilon} n_{m + i + lT_\epsilon}

@@

                \sum_{i = 0}^{J - 1}p_i \le \sum_{i = 0}^{J} n_i &\le 
                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} \left\lceil 

@@

                \right\rceil. 
            Note that $n_0 = 0$. 

@@

        The final results from above theorem provides the convergence rate of iterates and the complexity of restart GMAPG under Assumption \ref{ass:q-growth-ch2}. 
        We denote $\kappa := L/\mu$. 
        \begin{theorem}[restarted GMAPG convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}
            Let $F = f + g$ satisfy Assumption \ref{ass:q-growth-ch2}. 
            Let $J$ be the total number of iteration performed to achieve accuracy in the outer loop.
            Let $K := \sum_{i = 0}^{J - 1}p_i$ be the total iterations. 
            Then, the maximum $K$ needed to achieve optimality $\Vert z_J - z_J^+\Vert \le \delta$ on the iterates is bounded by $\mathcal O\left(\frac{1}{\sqrt{\kappa}}\ln\left(\frac{1}{\kappa\delta}\right)\right)$. 

@@

            Suppose $K = \sum_{i = 0}^{J - 1} p_i$ iteration were performed and, it achieved $G_0^{(J)} \le \epsilon$, 
            Now, let $k > 0$ and let $\epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)$ then: 
                &= 2(k - 1). 
                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}}\left\lceil 
                    \ln\left(
                \right\rceil - K
                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}}\left\lceil 
                    2(k - 1)
                \right\rceil - K 
                \frac{8\sqrt{2L(1 + e)}}{\sqrt{\mu}} (2(k - 1) + 1) - K
                0 &\le k - 1 + 1/2 - \frac{K\sqrt{\mu}}{16\sqrt{2L(1 + e)}}
                &\le k - \frac{K\sqrt{\mu}}{16\sqrt{2L(1 + e)}} .
            This gives us 
                G_0^{(J)} &\le \epsilon = \sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k + 1)
                e\sqrt{2}(F(z_0) - F^+)^{1/2}\exp(-k)
                e\sqrt{2}(F(z_0) - F^+)^{1/2}\exp\left(
                    - \frac{K\sqrt{\mu}}{16\sqrt{2L(1 + e)}}
                &= e\sqrt{2}(F(z_0) - F^+)^{1/2}\exp\left(
                    - \frac{K\sqrt{\kappa}}{16\sqrt{2 + 2e}}
            The above inequality shows a linear convergence rate of the quantity $G_0^{(J)}$ with respect to the total number of iterations required for GMAPG. 
            Using Theorem \ref{thm:qfg-peb-equiv} from previous chapter and take note that Assumption \ref{ass:q-growth-ch2} is Definition \ref{def:necoara-weaker-scnvx}\ref{def:necoara-qfg}. 
            Denote $z_J^+ = \Pi_{X^+}z_J$ then it has 
                G_0^{(J)} 
                &\underset{\text{(a)}}{=}\left\Vert \sqrt{L_0^{(J)}} \left(z_J - x_0^{(J)}\right) \right\Vert 
                = \frac{1}{\sqrt{L_0^{(J)}}} \left\Vert 
                    L_0^{(J)}\left(
                        z_J - x_0^{(J)}
                \right\Vert
                \underset{\text{(a)}}{=}\frac{1}{\sqrt{L_0^{(J)}}} \left\Vert 
                    \mathcal G_{1/L_0^{(J)}}(z_J)
                \right\Vert
                &\underset{\text{(b)}}{\ge} \frac{1}{\sqrt{2L}}\left\Vert\mathcal G_{1/L_0^{(J)}}(z_J)\right\Vert
                &\underset{\text{(c)}}{\ge} \frac{\sqrt{L(\mu + L)} - L}{\sqrt{L(\mu + L)}} \frac{1}{\sqrt{2L}}\left\Vert
                    z_J - z_J^+
                \right\Vert
                &= \frac{1}{\sqrt{2L}}\left(
                    1 - \frac{1}{\sqrt{1 + \mu/L}}
                \right)\left\Vert
                    z_J - z_J^+
                \right\Vert
                &\underset{\text{(d)}}{\ge} \frac{1}{2\sqrt{L}}\left(
                    \frac{\mu}{2L}
                \right)\left\Vert
                    z_J - z_J^+
                \right\Vert 
                = \frac{\kappa}{4\sqrt{L}} \left\Vert
                    z_J - z_J^+
                \right\Vert. 
                \item [(a)] 
                \item [(b)]
                \item [(c)]
                \item [(d)]
            It then yields the convergence rate of 
                \left\Vert z_J - z^+_J\right\Vert 
                &\le \frac{4eL\sqrt{2}(F(z_0) - F^+)^{1/2}}{\kappa}
                \exp\left(
                    - \frac{K\sqrt{\kappa}}{16\sqrt{2 + 2e}}
                \mathcal O\left(
                    \kappa^{-1}\exp\left(-\sqrt{\kappa}K\right)
            To achieve accuracy $\Vert z_J - z^+_J\Vert \le \delta$, it would require $\mathcal O\left(\frac{1}{\sqrt{\kappa}}\ln\left(\frac{1}{\kappa\delta}\right)\right)$ many total iterations of GMAGP. 
